The globular cluster system of the Auriga simulations

### 2020-04-08 response_to_referee.tex

\section*{Additional major comments}
\begin{itemize}
\item TODO justify the modelling philosophy.
\item We added a section 5.3 to discuss how our results change if we adopt an
age cut of 8 or 6 Gyr instead of 10 Gyr.
\item We clarified that the number of observed GCs differs between Figure 1 and 
Figure 2 because the latter shows metallicities between -2.5 and 0, galactocentric 
radii between 1 and 250 kpc. Figure 1, on the other hand, shows the full range
of radii, and the top panel of Figure 3 shows the full range of metallicities.
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, the half-mass stellar radius, etc). The simulations show a wide variety 
between properties of the Auriga galaxies with little correlation between these 
different stellar length scales. Therefore we could introduce unknown biases by 
normalising to any one of these options which is why we use the virial radius instead.
\item TODO: ``Discussion on the implications for the formation and evolution of clusters
    often feels a bit out of place and forced.''

\end{itemize}

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 2 -}
\begin{itemize}
\item We added the halo mass range of the Auriga simulations.
\item The last paragraph should now make more sense after updating the introduction.
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
\item Section 3.2 has been restructured.
\item We removed the standard error on the mean and replaced `dispersion' 
by `standard deviation' in section 3.3.
\item We added a sentence to clarify the last statement in section 3.4.
\end{itemize}

### 2020-04-08 AurigaGCS.tex
Comments on Section 2
Comments on Section 3

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised Bologna catalogue (RBC~5, last updated
August, 2012) is the latest edition of three decades of systematically
collecting integrated properties of the GCS of M31 \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the MW GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$r_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. We use CR16 because it is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study and it includes GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, the two radial distributions are not statistically
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

>>>>

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
were selected from the \mbox{\textsc{eagle}} DM only box, see 
\citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

@@

\subsection{Andromeda}
\label{sec:andromeda}
\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
present a uniform set of spectroscopic observations of the inner 
$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
the work of H14 is incorporated in the latest public release\footnote{Last 
revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
because it is the most recent aggregated dataset of M31's GCS that contains GCs 
in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
from the observed positions RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
in the Local Group host similar GC systems. However, the radial distributions of
the GCS of the MW and M31 are not statistically consistent with being drawn from 
the same underlying distribution due to substantial differences at intermediate radii.
